A systematic search for transiting planets in the \KT\ data

### 2015-03-16 ms.tex
adding figure describing overfitting

\response{Blah blah}

@@

>>>>

@@

\response{%
The choice to use 150 basis functions is largely arbitrary and we make no
claims of optimality.
This value was chosen as a trade-off between the computational cost of the
search---the cost scales as the third power of the size of the basis---and the
predictive power of the model.
In some preliminary experiments, we found that using a larger basis did, as
expected, lead to a marginally higher sensitivity to small transit signals
but the gain wasn't sufficient to justify the added cost.
}
